project-plan

### 2025-10-02 project-plan.qmd
Adding comments from coordinator

---
title: "project-plan"
date: today 
bibliography: bibliography.bib
csl: vancouver.csl
format: html
---
Introduction
============
Injury has reached epidemic proportions worldwide, disproportionately affecting the most productive and the youngest
members of society. Trauma, often synonymously used with serious injury, is defined as a physical injury and the
body's associated response [@Cao]. Furthermore, trauma remains a leading cause of death and disability
worldwide, where it is the foremost cause of death among people under the age of 45 and ranks as the fourth leading
cause of death across all ages [@Maerz2009].

>>>>

---
title: "project-plan"
date: today 
bibliography: bibliography.bib
csl: vancouver.csl
format: html
---
<!-- CP: The report is interesting, very promising and also well written. 
Effort is needed to further improve the report by structuring it in relation to the aims. Aims also to be improved according to the course i.e. challenging a scientific question (possibly having a hypothesis) in a yes/no manner: see comments
I might have missed some points in the report not being a clinician working on this matter but I think that you can improve the structure of the Aims and M&M a bit more. -->

Introduction
============
Injury has reached epidemic proportions worldwide, disproportionately affecting the most productive and the youngest
members of society. Trauma, often synonymously used with serious injury, is defined as a physical injury and the
body's associated response [@Cao]. Furthermore, trauma remains a leading cause of death and disability
worldwide, where it is the foremost cause of death among people under the age of 45 and ranks as the fourth leading
cause of death across all ages [@Maerz2009].
